---
output:
  html_document:
    code_folding: hide
---
<style type="text/css">
html {
  scroll-behavior: smooth;
}
</style
<br><br>
<center><h1><b>QE CDA course final project</b></h1>
<h4>By: Dovydas Riazanovas<br>
Finalized: 2020-05-27<br>
<small>Graded by Vaidotas Zemlys, final score: <b>10/10</b>.</small></h4></center>
<br><br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center> <h3><b>Our task</b></h3>
<a style="text-decorations:none; color:inherit" href="#p1">
1.Pick one country of your choice.<br>
2.Combine all of the data to one data.frame.<br></a>
<a style="text-decorations:none; color:inherit" href="#p3">
3.Do an exploratory analysis of the data.<br></a>
<a style="text-decorations:none; color:inherit" href="#p4">
4.Make a simple model which explains mobility changes with COVID-19 case data.<br>
5.Do several models with different mobility indicators.<br></a>
<a style="text-decorations:none; color:inherit" href="#p6">
6.Use generated models for forecasting.<br></a>
<a style="text-decorations:none; color:inherit" href="#p7">
7.Pick another, similar, country and compare. 
</center><br></a>


<div class="main" id="p1"><center><h3><b>Our data</b></h3></center></div>
<br>
First, we import libraries, that will be used in our project.
```{r library, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(rmarkdown)
library(AER)
library(ggplot2)
library(sjPlot)
library(gridExtra)
library(corrplot)
library(data.table)
```
Second, we import the data sets, used in our project:<br>
1.COVID-19 case data, provided by John Hopkins Unversity ( <a href="https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series">view</a> ).<br>
2.Google mobility data, provided by Google ( <a href="https://www.google.com/covid19/mobility/">view</a> ).<br>
3.Effective reproduction rate R data, provided by Simas Kucinskas ( <a href="http://trackingr-env.eba-9muars8y.us-east-2.elasticbeanstalk.com/">view</a> ).<br>
And, after minor tweaks in our data sets, we merge it to one data.frame called <i>all_data</i>.
```{r data set}
#Importing all data
confirmed <- read.csv('https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv')
deaths <- read.csv('https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv')
recovered <- read.csv('https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv')
mobility <- read.csv("https://raw.githubusercontent.com/vzemlys/cda_course/master/data/final_project/Global_Mobility_Report.csv")
reproduction_rate <- read.csv('https://raw.githubusercontent.com/vzemlys/cda_course/master/data/final_project/database_20200513_061217.csv')

#Tweaking covid-19 data:
confirmed <- confirmed %>% pivot_longer(cols = starts_with("X"), names_to = "Date")
deaths <- deaths %>% pivot_longer(cols = starts_with("X"), names_to = "Date")
recovered <- recovered %>% pivot_longer(cols = starts_with("X"), names_to = "Date")
#These three functions change the covid-19 data format to long.
names(confirmed)[names(confirmed) == "value"] <- "Confirmed_cases"
names(deaths)[names(deaths) == "value"] <- "Deaths"
names(recovered)[names(recovered) == "value"] <- "Recovered_cases"
#Additional name change in data.
covid <- confirmed %>% 
  inner_join(deaths %>% select(-Lat,-Long,-Province.State), by = c("Country.Region", "Date")) %>% 
  inner_join(recovered %>% select(-Lat,-Long,-Province.State), by = c("Country.Region", "Date"))
#Merge 3 covid-19 data's to one.
covid$Date <- as.Date(covid$Date, "X%m.%d.%y") # date format
covid$Death_rate<-covid$Deaths/covid$Confirmed_cases #generate the Death_rate.
covid$Death_rate[is.nan(covid$Death_rate)] <- 0 # Generating NaN values to 0 (since division by 0 at start of data occurs)

covid <- covid[, c(5, 2, 6, 8, 9 )] # only these columns are usefull to us.
covid$Country.Region<-as.character(covid$Country.Region) 

covid$C_Confirmed_cases<-c(0,diff(covid$Confirmed_cases)) 
covid$C_Recovered_cases<-c(0,diff(covid$Recovered_cases))
# the difference will be used in exploratory data.

#Tweaking mobility data:
mobility <- mobility[mobility$sub_region_1 == "",] # we use only the average, not going into regions.
mobility = mobility[,c(5, 2, 6, 7, 8, 9, 10, 11)] # only these columns will be usefull to us.
names(mobility)[names(mobility) == "country_region"] <- "Country.Region"
names(mobility)[names(mobility) == "date"] <- "Date"
mobility$Date <- as.Date(mobility$Date, "%Y-%m-%d")
mobility$Country.Region<-as.character(mobility$Country.Region)
mobility$Mobility<-(mobility$retail_and_recreation_percent_change_from_baseline
                     +mobility$grocery_and_pharmacy_percent_change_from_baseline
                     +mobility$parks_percent_change_from_baseline
                     +mobility$transit_stations_percent_change_from_baseline
                     +mobility$workplaces_percent_change_from_baseline
                     +mobility$residential_percent_change_from_baseline)/6
#We estimate the average change in mobility (this will be usefull during the simple model estimation)


#Tweaking reproduction rate data:
reproduction_rate$Date <- as.Date(reproduction_rate$Date, "%Y-%m-%d")
reproduction_rate=group_by(reproduction_rate, Date, Country.Region) %>% summarize("R" = mean(R)) # lets view only the average R at time period T.
reproduction_rate$Country.Region<-as.character(reproduction_rate$Country.Region)


#Merging 3 data sets in to our main data.frame -> all_data
all_data <- covid %>% 
  inner_join(reproduction_rate, by = c("Date", "Country.Region")) %>% 
  inner_join(mobility, by = c("Date", "Country.Region"))

all_data <- all_data %>% 
  rename( 
    C_Retail = retail_and_recreation_percent_change_from_baseline,
    C_Shopping = grocery_and_pharmacy_percent_change_from_baseline,
    C_Parks = parks_percent_change_from_baseline,
    C_Transit = transit_stations_percent_change_from_baseline,
    C_Workplace = workplaces_percent_change_from_baseline,
    C_Residential = residential_percent_change_from_baseline )
  
rm(covid);rm(reproduction_rate);rm(mobility);rm(confirmed);rm(deaths);rm(recovered) 
# this is just to optimize the data.

```
Eventually, we use <b>Lithuania</b> for our analysis.<br>
The data.frame for this country can be seen bellow.<br>
<small><i>1) Date - given time period. 2) Country.Region - country of interest. 3) Confirmed_cases - confirmed COVID-19 cases.<br>
4) Recovered_cases - recovered COVID-19 cases. 5) Death_rate - death rate of virus. 6) C_Confirmed_cases - change in confirmed cases.<br>
7) C_Recovered_cases - change in recovered cases. 8) R - Effective reproduction rate. 9) C_Retail - Mobility trends for Retail services.<br>
10) C_Shopping - Mobility trends for food stores, pharmacies. 11) C_Parks - Mobility trend for public places. 12) C_Trends - Mobility trends for public transportation hubs.<br>
13) C_Workplace - Mobility trends for places of work. 14) C_Residential - Mobility trends for places of residence. 15) Mobility - average mobility trend</i></small>
```{r Lithuania, echo=FALSE}
Country = "Lithuania"
Country <- all_data[grep(Country, all_data$Country.Region),]
Country %>% paged_table
```
<div class="main" id="p3"><center><h3><b>Our exploratory analysis</b></h3></center></div>
We view the summary of our data.
```{r summarydata1}
summary(Country)
```
We see, that the min. change in confirmed cases is <i>-105.00</i> and the max. is <i>90.00</i>. This shows a small change in confirmed cases, compared to big countries.<br>
Futhermore, the mobility levels are very low,and mostly negative in: <i>C_Retail,C_Shopping,C_Transit,C_Workplace</i>.
This states, that people, living in Lithuania, were effected by the pandemic.<br>
<br>

Secondly, lets view graphs, that represent the change in COVID-19 cases compared to mobility trends.<br>
<small><i>
1) <font color="black">Black line</font> - change in confirmed cases.
2) <font color="red">Red line</font> - mobility indicator for retail services.
3) <font color="#ADA96E">Haki line</font> - mobility indicator for food stores & pharmacies<br>
4) <font color="blue">Blue line</font> - mobility indicator for public places.
5) <font color="orange">Orange line</font> - mobility indicator for public transport hubs.
6) <font color="brown">Brown line</font> - mobility indicator for places of work.<br>
7) <font color="violet">Violet line</font> - mobility indicator for places of residence.
</i></small>
<br><br>
<center>
```{r plots1,echo=FALSE}
p1 <- 
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Retail), color="red") +
  labs(subtitle = "Retail services") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())

p2 <- 
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Shopping), color="#ADA96E") +
  labs(subtitle = "Food stores and pharmacies") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p3 <-
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Parks), color="blue") +
  labs(subtitle = "Public places (parks, beaches, etc.)") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p4 <-
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Transit), color="orange") +
  labs(subtitle = "Public transport hubs") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p5 <-
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Workplace), color="brown") +
  labs(subtitle = "Places of work") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p6 <-
  ggplot(Country, aes(x=Date)) + 
  geom_line(aes(y = C_Confirmed_cases), color = "black") + 
  geom_line(aes(y = C_Residential), color="violet") +
  labs(subtitle = "Places of residence") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())

grid.arrange(p1,p2,p3,p4,p5,p6, top = "Change in COVID-19 cases compared to mobility trends for:",
             layout_matrix = matrix(c(1,2,3,4,5,6), ncol=2, byrow=TRUE,))
#We arrange 6 plots ,to fit in 2 columns and plot them.
```
</center><br>
We see, that over time there is a minor decrease in the change of COVID-19 cases and a minor increase in the mobility levels of: retail services, public transport hubs and Food stores & pharmacies. This is because the government is relaxing quarantine rules & restrictions, based on the decrease in change of COVID-19 cases.
<br>
We also see, that from the start the mobility level of Public places has increased rapidly. This is because government based restrictions stimulated citizens to engage in outdoor activities (most of the time in public places), rather than indoor activities.
<br>
Finally, we see, that the mobility levels of Places of work and Places of residence are stable - practically no differences during our given time period.
<br><br>
Thirdly, we view graphs, that represent COVID-19 data and the effective reproduction rate.<br><br>
<center>
```{r plots2,echo=FALSE}

#ALSO PLOT FOR R and RECOVERED CASES
p7 <- ggplot(Country,aes(x=Date))+
  geom_line(aes(y=R),color="red")+
  labs(subtitle = "Effective reproduction rate") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p9 <- ggplot(Country,aes(x=Date))+
  geom_line(aes(y=Death_rate),color="violet")+
  labs(subtitle = "Death rate") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())
p10 <- ggplot(Country,aes(x=Date))+
  geom_line(aes(y=Recovered_cases),color="orange")+
  labs(subtitle = "Recovered cases") +
  theme (axis.title.x = element_blank(),axis.title.y = element_blank())

grid.arrange(p7,p9,p10, top = "COVID-19 data and the effective reproduction rate",
             layout_matrix = rbind(c(1),c(2,3)))
```
</center><br>
<B>REMINDER:</b> The effective reproduction rate measures the intensity of the epidemic.<br>
We see, that during our given time period the death rate and recovery cases increase, leading to a decrease in the effective reproduction rate. In other words, a decrease in people being sick (the outcomes are death or recovery), decreases the intensity of the epidemic.<br>
<br><br>
To approve statements made from graph analysis, we view the correlation tables:<br>
<center>
```{r corplot, echo=FALSE}
par(mfrow=c(1,2))
corrplot(Country %>% select(Confirmed_cases,C_Retail,C_Shopping, C_Parks, C_Transit, C_Workplace, C_Residential) %>% cor(use = "pairwise"), method = "number",cl.pos = "n") # Correlation plot for 2nd
corrplot(Country %>% select(R,Recovered_cases,Death_rate) %>% cor(use = "pairwise"), method = "number",cl.pos = "n") # Correlation plot for 3rd

```
</center>
For the first correlation table we see, that the change of confirmed cases are negatively correlated with all of the mobility levels, except for the mobility levels of places of work and places of residence - these mobility levels have close to no correlation.<br>
For the second correlation table We see, that R (the effective reproduction rate) is negatively correlated with both the death rate and recovered cases.
<br><br>
<div class="main" id="p4"><center><h3><b>Our generated models</b></h3></center><br></div>

1) Simple linear model of the average mobility trend (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).

```{r genmodel}
genmodel <- lm(Mobility~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
```
<center>
```{r tabgenmodel,echo=FALSE}
tab_model(genmodel)
```
</center><br>
Using the summary model we see, that only the recovered cases variable is statistically significant and since the R squared is 0.531, the model is good for analyzation. Thus, we can state, that the change of the average mobility trend is caused by recovered cases.<br><br>

2) Linear model of the retail services mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
3) Linear model of the food stores & pharmacies mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
4) Linear model of the public places mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
5) Linear model of the public transportation hubs mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
6) Linear model of the places of work mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
7) Linear model of the places of residence mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).
```{r othmodels}
model1 <- lm(C_Retail~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model2 <- lm(C_Shopping~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model3 <- lm(C_Parks~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model4 <- lm(C_Transit~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model5 <- lm(C_Workplace~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model6 <- lm(C_Residential~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
```
<center>
```{r tabothm, echo=FALSE}
tab_model(model1, model2, model3, model4,model5,model6, p.style = "asterisk", show.ci = FALSE)
```
</center><br>
Using our summary table for all other models we see the recovered cases variable is statistically significant only in model 2,4,5,7. In models 3 and 6 our independent variables are not significant. Thus, we can state, that our COVID-19 data can explain only the mobility indicators of: retail services, public places, public transportation hubs and places of residence. We can also see, that the best model is model 2, since it has the highest R squared value of 0.721 and the worst model is model 6, since it has the lowest R squared value of 0.112.
<br><br>
<div class="main" id="p6"><center><h3><b>Forecasts</b></h3></center><br></div>
After generating forecasts, using our models, we created a data table for comparing forecasted values and actual values.
```{r prediction}
prediction0 <- predict(genmodel, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction1 <- predict(model1, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction2 <- predict(model2, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction3 <- predict(model3, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction4 <- predict(model4, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction5 <- predict(model5, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction6 <- predict(model6, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")

comparison <- data.table(Country[(nrow(Country)-6):nrow(Country),1]," " = c("     "), 
                 Country[(nrow(Country)-6):nrow(Country),15], "Predicted" = prediction0[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),9], "Predicted" = prediction1[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),10], "Predicted" = prediction2[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),11], "Predicted" = prediction3[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),12], "Predicted" = prediction4[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),13], "Predicted" = prediction5[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),14], "Predicted" = prediction6[,1])
```
<center>
```{r view,echo=FALSE}
comparison %>% paged_table
```
</center><br>
We see, that the most accurate forecast is for the retail services mobility indicator, and this is because our generated model 2 is the best generated model (as seen earlier). The least accurate forecast is for the places of work mobility indicator, since it it the worst generated model (as seen earlier).<br>
In conclusion, our forecasts for the mobility indicators of retail service and public transportation hubs are accurate and can be used for wider analyzation, but they are not perfect. The other forecasts generate large forecast errors and should not be used for wider analyzation.

<br><br>
<div class="main" id="p7"><center><h3><b>Comparison</b></h3></center><br></div>
We pick Estonia, as a similar country to Lithuania, since the size of both countries and the economic indicators are similar.<br>
Below you can see the data.frame for Estonia.
<center>
```{r Estonia, echo=FALSE}
Country = "Estonia"
Country <- all_data[grep(Country, all_data$Country.Region),]
Country %>% paged_table
```
</center></br>
We now generate <b>identical</b> linear models for Estonia and plot our summary table.<br>
<small><b>These are our generated models:</b></br>

1) Simple linear model of the average mobility trend (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
2) Linear model of the retail services mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
3) Linear model of the food stores & pharmacies mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
4) Linear model of the public places mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
5) Linear model of the public transportation hubs mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
6) Linear model of the places of work mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).<br>
7) Linear model of the places of residence mobility indicator (dependent variable) and confirmed cases+recovered cases+death rate (independent variables).

</small>
```{r modelsagain}
genmodel <- lm(Mobility~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model1 <- lm(C_Retail~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model2 <- lm(C_Shopping~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model3 <- lm(C_Parks~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model4 <- lm(C_Transit~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model5 <- lm(C_Workplace~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
model6 <- lm(C_Residential~Confirmed_cases+Recovered_cases+Death_rate,data=Country)
```
<center>
```{r sumtableestonia,echo=FALSE}
tab_model(genmodel, model1, model2, model3, model4,model5,model6, p.style = "asterisk", show.ci = FALSE)
```
</center><br>
Using the summary table we see, that in models 1, 6 and 7 only the recovered cases variable is statistically significant. In models 2 and 5 all of our independent variables are statistically significant. In model 3 confirmed cases and death rates are statistically significant. Finally, in model 4 we have no significant independent variables. The best model is model 2, since it has the highest R squared value of 0.584. The worst model is model 6, with an extremely low R squared value of 0.091.<br><br>
<b>Comparing</b> to our Lithuanian models, we can state, that mobility trends in Estonia are caused not only by the recovered cases, but also by confirmed cases and death rates. COVID-19 data can explain more Estonian mobility indicators, then Lithuanian. We can also see similarities between models,since both for Lithuania and Estonia, the best model is model 2 and the worst model is model 6. We can also point out, that the Lithuanian model 2 is better than the Estonian model 2, since 0.721 <i>(R squared for Lithuanian model 2)</i> <b>></b> 0.584 <i>(R squared for Estonian model 2)</i>.
<br><br>
Finally, we generate <b>identical</b> forecasts for Estonia and create a data table for comparing forecasted values and actual values.
```{r prediction2}
prediction0 <- predict(genmodel, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction1 <- predict(model1, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction2 <- predict(model2, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction3 <- predict(model3, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction4 <- predict(model4, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction5 <- predict(model5, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")
prediction6 <- predict(model6, newdata= Country[(nrow(Country)-6):nrow(Country), ], interval="confidence")

comparison <- data.table(Country[(nrow(Country)-6):nrow(Country),1]," " = c("     "), 
                 Country[(nrow(Country)-6):nrow(Country),15], "Predicted" = prediction0[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),9], "Predicted" = prediction1[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),10], "Predicted" = prediction2[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),11], "Predicted" = prediction3[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),12], "Predicted" = prediction4[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),13], "Predicted" = prediction5[,1]," " = c("     "),
                 Country[(nrow(Country)-6):nrow(Country),14], "Predicted" = prediction6[,1])
```
<center>
```{r view2,echo=FALSE}
comparison %>% paged_table
```
</center><br>
We see, that the most accurate forecast is again the retail services mobility indicator and the least accurate forecast is the places of work mobility indicator.<br>
Our forecasts for the mobility indicators of retail service, food stores & pharmacies, public transportation hubs are accurate,but not perfect. Other forecasts generate large forecast errors.<br><br>
<b>Comparing</b> to Lithuanian forecasts we can see, that Estonian forecasts can predict more mobility indicators. On the other hand, Lithuanian forecasted mobility indicators for both retail service and public transportation hubs are better for forecasting, since they have a smaller forecast error.<br><br>
<b>Conclusion</b><br>
We can state, that forecasts and linear models generate different results, when choosing different (even similar) countries. The main reasons to this are:<br>
1) Different country governments react differently during the time of a pandemic. This leads to different restrictions and different citizen behavior.<br>
2) Different countries have different quantities of confirmed,recovered and death cases, leading to different independent variables and thus, different results.
